Sample-efficient Reinforcement Learning with Latent Representations

### 2024-01-31 paper/main.tex

  % Draw backgrounds
  \begin{pgfonlayer}{background}
    \draw[draw=none,fill=black!10,rounded corners=5pt] ($(i0.north west) + (-.5cm,1cm)$) 
      rectangle ($(i2.east)!(z2.north)!(i2.east) + (.5cm,-1cm)$);
  \end{pgfonlayer}

>>>>

  % Draw backgrounds
  \begin{pgfonlayer}{background}

    \coordinate (mid) at ($(i2.east)!.5!(policy.west)$);

    \draw[draw=none,fill=black!10,rounded corners=5pt] ($(i0.north west) + (-.25cm,1cm)$) 
      rectangle ($(mid)!(z2.north)!(mid) + (-3pt,-1cm)$);

    \draw[draw=none,fill=black!05,rounded corners=5pt] ($(mid)!(i2.north east)!(mid) + (3pt,1cm)$) 
      rectangle ($(value.east)!(z2.north)!(value.east) + (.25cm,-1cm)$);

  \end{pgfonlayer}
